|

### 2023-01-31 paper_comparison/paper_comparison/paper_comparison.Rmd
update heter shape section

Shape of the non-linearity pattern is a primary factor contributes to the non-linearity model. With different non-linearity patterns, it is expected that the visual test will respond variously.

According to Figure \ref{fig:poly-power-uniform-j}, conventional tests have almost identical power in testing the "U", the "S" and the "M" shape, except for testing the "Triple-U" shape, which have significantly lower power. To understand why this is, one needs to return to the way the RESET test is applied. It requires a parameter indicating degree of fitted values to test for, and the recommendation is to generically use four (@ramsey_tests_1969). However, the "Triple-U" shape constructed from the Hermite polynomials use power up to 18. If the RESET test had been applied using a higher power no less than six, the power curve of "Triple-U" shape will have little difference to other shapes. The recommendation of the polynomial power for the RESET should be revised, perhaps. This illustrates the sensitivity of conventional testing to the parameters, and it also points to a limitation that one needs to know the data structure in order to set the parameters for the test.

For visual tests, we expect the "U" shape will be the easiest one to be detected by subjects followed by the "S", "M" and "Triple-U" shape. From Figure \ref{fig:poly-power-uniform-j}, it can be observed that the power curves are mostly aligned with our expectation, except for the "M" shape. Interestingly, the "M" shape is as easy to be detected as the "U" shape, which implies the readability of the shape do not strictly follow the degree of the polynomials.

@@

We also investigate the impact of different heteroskedasticity patterns. In theory, the "Left-triangle" and the "Right-triangle" should have little difference from the point of view of a Breusch-Pagan test. According to Figure \ref{fig:heter-power-uniform-a}, this is indeed the case. 
Similarly, these two shapes should have the same visual test power, unless the orientation of the visual pattern is a non-negligible factor from human perspective. However, it can be observed from Figure \ref{fig:heter-power-uniform-a} that the power curve for the "Left-triangle" shape is constantly higher than the one for the "Right-triangle" shape, indicating a potential favour of orientation by human, which is worth to be explored in future studies.

The "Butterfly" shape

>>>>

A primary factor contributes to the non-linearity model is the shape of the non-linearity. According to Figure \ref{fig:poly-power-uniform-j}, conventional tests have almost identical power in testing the "U", the "S" and the "M" shape, except for testing the "Triple-U" shape, which have significant lower power. To understand why this is, one needs to return to the way the RESET test is applied. It requires a parameter indicating degree of fitted values to test for, and the recommendation is to generically use four (@ramsey_tests_1969). However, the "Triple-U" shape constructed from the Hermite polynomials use power up to 18. If the RESET test had been applied using a higher power no less than six, the power curve of "Triple-U" shape will have little difference to other shapes. The recommendation of the polynomial power for the RESET should be revised, perhaps. This illustrates the sensitivity of conventional testing to the parameters, and it also points to a limitation that one needs to know the data structure in order to set the parameters for the test.

For visual tests, we expect the "U" shape will be the easiest one to be detected by subjects followed by the "S", "M" and "Triple-U" shape. From Figure \ref{fig:poly-power-uniform-j}, it can be observed that the power curves are mostly aligned with our expectation, except for the "M" shape, which is as easy to be detected as the "U" shape. This implies the readability of the shape do not strictly follow the degree of the polynomials.

@@

We also investigate the impact of different heteroskedasticity shapes on power of conventional tests and visual tests. In theory, the "Left-triangle" and the "Right-triangle" shapes are functionally identical from the point of view of a Breusch-Pagan test. As shown in Figure \ref{fig:heter-power-uniform-a}, this is indeed the case where little difference between the power curves can be perceived. 
Similarly, visual tests will have the same power of detecting these two shapes if they are equally likely to be identified. However, it can be observed from Figure \ref{fig:heter-power-uniform-a} that the power curve for the "Left-triangle" shape is constantly higher than the one for the "Right-triangle" shape, indicating a potential favour of orientation by human, which is worth to be explored in future studies.

The "Butterfly" shape on the other hand seems to be
